### 2021-06-18 README.Rmd
run all models on HiperGator sucessfully
update readme

-   Open the project in RStudio by double-clicking the `HeliconiaDemography.Rproj` file.
-   Install the [`renv` package](https://rstudio.github.io/renv/articles/renv.html) if it's not already installed and run `renv::restore()` to install all package dependencies.
-   Install the [`targets` package](https://docs.ropensci.org/targets/).
-   Run `targets::tar_make()` from the R console to run all code and produce all outputs.

## Notes

>>>>

-   Open the project in RStudio by double-clicking the `HeliconiaDemography.Rproj` file.
-   Install the [`renv` package](https://rstudio.github.io/renv/articles/renv.html) if it's not already installed and run `renv::restore()` to install all package dependencies.
-   Install the [`targets` package](https://docs.ropensci.org/targets/).
-   Run `targets::tar_make()` or `targets::tar_make_clustermq()` from the R console to run all code and produce all outputs.

**NOTE**: The full pipeline will take a *very long* time to run.  I suggest switching off individual-level random effects (more details in comments in `_targets.R`) if you want to run the project on your own computer.  Without individual-level random effects the pipeline should run relatively quickly (< 1hr, I think).

## Additional Dependencies
